\documentclass[10pt]{article}

\usepackage{calc}

\usepackage{ifpdf}

\ifpdf
  \usepackage[pdftex]{hyperref}
\else
  \usepackage[hypertex]{hyperref}
\fi

\hypersetup{
letterpaper,
colorlinks,
urlcolor=blue,
pdfpagemode=none,
pdftitle={Curriculum Vitae},
pdfauthor={NJP},
pdfcreator={$ $Id: cv.tex, 2008/01/13 01:38:31 dscape $ $},
pdfsubject={Personal Resume of Nuno Job Pinto},
pdfkeywords={nuno job pinto,
nuno job,
nuno pinto,
minho, 
uminho, 
braga,
porto,
university of minho,
universidade do minho,
resume, 
curriculum,
cv,
curriculum vitae,
cryptography,
XML,
mobicomp,
.NET,
IMC,
versit,
vCard,
vCalendar,
SyncML,
regular expressions,
regexp,
mobile,
symbian,
haskell,
PURe,
DOM,
VSTO,
PHP,
DB2,
IBM,
Ambassador,
DB2 Ambassador,
CAOS,
ETAPS,
office,
vsto,
visual studio tools for office,
msc,
bs,
bsc,
ruby,
rails,
ruby on rails,
restfull,
rest,
C,
CSS,
HTML,
java,
LaTeX,
XForms,
csharp,
javascript,
prolog,
SQL,
UML,
XQuery,
XSL,
XSLT,
DTD,
XSD,
Schemas,
yaml,
macos,
mac os x,
os x,
leopard,
macosx,
mac-os-x,
linux,
ubuntu,
fedora,
windows,
windows xp,
windows vista,
windows nt,
ETAPS,
OPENGL,
Glassfish,
Flash,
Illustrator,
Photoshop,
SOAP,
MySQL,
Usability,
Open Source,
CouchDB,
RubyForge,
FOSS,
SVN,
Security,
web design,
web,
software,
web developer,
web development,
developer,
portugal,
europe}}

\reversemarginpar

\usepackage[paper=letterpaper,
            marginparwidth=1.2in,     
            marginparsep=.05in,      
            margin=1in,              
            includemp]{geometry}

%% Use these lines for A4-sized paper
%\usepackage[paper=a4paper,
%            %includefoot, % Uncomment to put page number above margin
%            marginparwidth=30.5mm,    % Length of section titles
%            marginparsep=1.5mm,       % Space between titles and text
%            margin=25mm,              % 25mm margins
%            includemp]{geometry}

\setlength{\parindent}{0in}

\usepackage{paralist}


\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\pagestyle{empty}      % Uncomment this to get rid of page numbers
\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\fancyfootoffset{\marginparsep+\marginparwidth}
\newlength{\footpageshift}
\setlength{\footpageshift}
          {0.5\textwidth+0.5\marginparsep+0.5\marginparwidth-2in}
\lfoot{\hspace{\footpageshift}%
       \parbox{4in}{\, \hfill %
                    \arabic{page} of \protect\pageref*{LastPage} % +LP
%                    \arabic{page}                               % -LP
                    \hfill \,}}

\usepackage{color,hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}

\newcommand{\makeheading}[1]%
        {\hspace*{-\marginparsep minus \marginparwidth}%
         \begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
                {\large \bfseries #1}\\[-0.15\baselineskip]%
                 \rule{\columnwidth}{1pt}%
         \end{minipage}}

\renewcommand{\section}[2]%
        {\pagebreak[2]\vspace{1.3\baselineskip}%
         \phantomsection\addcontentsline{toc}{section}{#1}%
         \hspace{0in}%
         \marginpar{
         \raggedright \scshape #1}#2}

\newenvironment{outerlist}[1][\enskip\textbullet]%
        {\begin{enumerate}[#1]}{\end{enumerate}%
         \vspace{-.6\baselineskip}}

\newenvironment{innerlist}[1][\enskip\textbullet]%
        {\begin{compactenum}[#1]}{\end{compactenum}}

\newcommand{\blankline}{\quad\pagebreak[2]}

\begin{document}
\makeheading{Nuno Job}

\section{Personal Information}

\newlength{\rcollength}\setlength{\rcollength}{1.85in}%

\begin{tabular}[t]{@{}p{\textwidth-\rcollength}p{\rcollength}}
	  35 Barker Ave \#4B         & Phone: +1 (914) 255-7157 \\
	  White Plains, NY 10601     & {\tt nunojobpinto@gmail.com} \\
\end{tabular}

\section{Profile}
\begin{innerlist}
	\item Positive, can-and-will-do, team player attitude. 
    \item Excellent communication and interpersonal skills.
    \item Ability to adapt in a challenging environment. Fast learner.
    \item Goal oriented with a high degree of energy and commitment.
    \item Creative with high attention to detail.
\end{innerlist}

\blankline

\section{Professional Experience}
%
\href{http://www.ibm.com/}{\textbf{IBM}}, 
Hawthorn, NY, USA
\begin{outerlist}

\item[] \textit{ISV Solutions Engineer - Data Specialist (co-op)}%
        \hfill \textbf{October 2009}
\begin{innerlist}
\item Customer enablement - PureXML prototyping and consulting for financial, healthcare and government institutions.
\item Lectured XQuery and SQL/XML for customers and partners.
\item Co-author and Team leader on an emerging technologies book on DB2 and Ruby on Rails.
\item Cross product integration \& whitespace exploration
\item Industry specific solutions using XML standards.
\end{innerlist}

\end{outerlist}

\blankline

\href{http://www.mobicomp.com/}{\textbf{Mobicomp} }, 
Braga, Portugal
\begin{outerlist}

\item[] \textit{Software Engineer (outsourcing)}%
        \hfill \textbf{October 2006 to March 2007}
\begin{innerlist}
\item Created the user interface and implemented the c\# client logic for the \href{http://myphone.microsoft.com}{MobileKeeper} Outlook Client. Developed a parser for the IMC personal data interchange formats (vCard and vCalendar). Acquired basic knowledge on the SyncML protocol.
\end{innerlist}

\end{outerlist}

\blankline

\textbf{\href{http://www.triplow.pt}{Triplow}}, 
Le\c ca da Palmeira, Portugal
\begin{outerlist}

\item[] \textit{Web Developer}%
        \hfill \textbf{May 2001 to October 2001}
\begin{innerlist}
\item Designed and implemented the \href{https://www.interportas.net}{Interportas Portal}.
\item Created templates for clients websites.
\end{innerlist}

\end{outerlist}

\section{Education}
\href{http://www.uminho.pt/Default.aspx?lang=en-US}{\textbf{University of Minho}}, 
Braga, Portugal

\begin{outerlist}

\item[] M.S., 
        \href{http://www.di.uminho.pt/teaching/graduate_courses/master-course-in-informatics/master-course-in-informatics?set_language=en&cl=en}
             {Computer Science} 
        (expected: November 2009)
        \begin{innerlist}
        \item Fields of Study: Web applications \& Web services, XML, Cryptography, Distributed Systems, Natural Language Processing
        \end{innerlist}

\item[] B.E., 
        \href{http://www.gri.uminho.pt/ModuleLeft.aspx?mdl=~/Modules/ECTS/PortalModules/Plans.ascx&c=53&mid=366&lang=eng&pageid=377&tabid=4}
             {Computer Science and Systems Engineering}, March 2008
\end{outerlist}

\blankline

\href{http://www.iha.dk}{\textbf{Engineering College of Aarhus}}, 
Aarhus, Denmark

\begin{outerlist}
	
\item[] Summer School - Bang \& Olufsen (B\&O) - Erasmus Intensive Program, 
        \href{http://www.iha.dk/English-5570.aspx}
             {Conceptual Design and Development of Innovative Products}, July 2008
	        \begin{innerlist}
	        \item Fields of Study: Innovation, Product Development and Prototyping
	        \end{innerlist}

\section{Achievements and activities} 
%
\href{http://www-306.ibm.com/software/data/db2/express/students.html}{IBM DB2 Student Ambassador}
\begin{innerlist}
	\item \href{http://www-306.ibm.com/software/data/db2/express/students.html}{Featured DB2 Student Ambassador}, December 2007
	\item Founder of the first \href{http://caos.di.uminho.pt/~db2}{Portuguese DB2 Students Group}, October 2007
\end{innerlist}

\blankline

\href{http://www.opensource.org}{Open-Source Collaborations}
\begin{innerlist}
	\item Open-Source Development for the CouchDB Ruby Driver, since March 2008
	\item Member of the \href{http://caos.di.uminho.pt}{Open Source Support Center}, since October 2007
	\item Several open-source applications hosted at \href{http://github.com/dscape}{github.com/dscape} 
\end{innerlist}

\blankline

\section{Skills}
\textbf{Languages}
\begin{innerlist}
	\item C\#, Haskell, Java, Ruby, Perl, Python, XForms, XQuery, XML, C++, Javascript, JSON, LaTeX, PHP, Prolog, SQL, SQL/XML, UML
\end{innerlist}

\blankline

\textbf{Database}
\begin{innerlist}
	\item DB2, PureXML, MySQL, SQLite, SolidDB, Oracle XML DB
	\item ORM, JDBC, Database security \& privacy
\end{innerlist}

\blankline

\textbf{Frameworks}
\begin{innerlist}
	\item .NET, VSTO.NET, OpenGL, Ruby on Rails
\end{innerlist}

\blankline

\textbf{Miscellaneous}
\begin{innerlist}
	\item XML Technologies: XQuery, XPath, Schema, Stylesheet, J2EE Web-Services (SOAP \& REST), XForms, Industry Formats.
	\item DB2 pureXML, Eclipse, Netbeans, Websphere Aplication Server, Rational Application Developer, IBM DataStudio.
	\item Open-Source \& Emerging Technologies. (e.g. RabbitMQ, event-driven Web-Services)
\end{innerlist}


\end{document}
